### 2014-03-14 src/discussion.Rnw
udpate
update

\begin{figure}[t]
\includegraphics[totalheight=5cm]{fig/opstrat1.eps}
\caption{Example Mutants}
\label{fig:egmutants}
\end{figure}

@@

We see three clear patterns in our results. The first is that sampling strategy
can predict the final score with very minimal loss in accuracy up to a fraction
of $\frac{1}{64}$ of the total number of mutants (Our experiments suggest up
to $70$ times reduction, with a low standard deviation of $6.72$). We did nto
cut off with the 99\% rule as mentioned by Zhang et al.~\cite{zhang2013ase}
(Originally proposed by Offutt et al.~\cite{offutt1996experimental} for a
different measurement), and instead chose to observe that we obtained
$R^2 > 0.96$ which provides a high confidence in the accuracy of prediction.

The second pattern is that fractional sampling based on projects appears to be
better than that based on classes, which inturn is better than methods and
lines, with regard to the stability of the result (i.e low sd), and correlation.
This seems not very visible at lower levels (where the reduction fraction is less
than 32), but becomes more pronounced as the mutant reduction fraction increases.
There seem to exist a hierarchy of sampling, where by as you go more fine grained,
the stability and correlation decreases. This is infact opposite to what Zhang
et al.~\cite{zhang2013ase} observed, where they found that $S_{meth}$ ourperforms
$S_{base}$.

The third pattern is that the simplest sampling scheme --- simple random sampling ---
performs best compared to sampling schems that tried to provide higher weightage
to specific elements based on specific criterias. More importantly, operator selection
seems to be generally worse off in predicting the final score than any of the random
selection schemes.

>>>>

%\begin{figure}[t]
%\includegraphics[totalheight=4.5cm]{fig/opstrat1.pdf}
%\caption{Mutant distribution in a sample project along operators and program elements}
%\label{fig:egmutants}
%\end{figure}

@@

We see a few patterns in our results. The first is that sampling strategy
can predict the final score with very minimal loss in accuracy up to a fraction
of $\frac{1}{64}$ of the total number of mutants (Our experiments suggest up
to $70$ times reduction, with a low standard deviation of $6.72$). We did not
cut off with the 99\% rule as mentioned by Zhang et al.~\cite{zhang2013ase}
(Originally proposed by Offutt et al.~\cite{offutt1996experimental} for a
different measurement), and instead chose to observe that we obtained
$R^2 > 0.96$ which provides a high confidence in the accuracy of prediction.

The second pattern is that fractional sampling based on projects appears to be
better than that based on classes, which in turn is better than methods and
lines, with regard to the stability of the result (i.e low sd).
This seems not very visible at lower levels (where the reduction fraction is less
than 32), but becomes more pronounced as the mutant reduction fraction increases.
There seem to exist a hierarchy of sampling, where by as you go more fine grained,
the stability decreases.
We did not see the pattern found by Zhang et al.~\cite{zhang2013ase} where by
the method based sampling had the highest accuracy. In fact, in our measurements,
the opposite may be true, with project based sampling getting the highest correlation
with the final score a majority of the time.

The third pattern is that the simplest sampling scheme --- simple random sampling ---
performs best compared to sampling schemes that tried to provide higher weight
to specific elements based on specific criteria. More importantly, operator selection
seems to be generally worse off in predicting the final score than any of the random
selection schemes.

% There may in fact be a simple reason for this observation. Consider the Figure~\ref{fig:egmutants}.
% It is a representation of the distribution of mutants along two orthogonal axes --- the
% mutation operators, and program elements such as classes. For the purposes of this
% explanation, assume that each classes contain equal number of lines, and each mutant
% produced per line by each of the mutation operators are marked by a small solid circle.
% The two solid vertical lines in blue and red represents two classes, one with a relatively
% small number of mutants and other with large number of mutants. Consider that we are sampling
% by class, and we are choosing all mutants for simplicity. Let $c$ be the number of classes.
% Here, a mutant in red class contributes to $1/n_{red}$ to the mean of the score of the
% red class, and the red class contributes $1/c$ to the total mean.  So the contribution of a
% mutant in red class to the complete is $1/(c * n_{red})$. Similarly for blue class.
% However, if the sampling is done on a complete project basis, then the contribution of any
% mutant is $\frac{1}{\sum_{i=1}^{c} n_{i}}$, which depending on the size of the class might
% be different from what it would contribute if sampling is used. To put it another way,
% for any kind of sampling used based on sub elements, the units in the sample gets equal
% weightage in contribution irrespective of the size of elements themselves, while if the sampling
% is done on a project basis, the contribution of sub elements depends on the number of mutants
% each elements produced.
% 
% What this is saying in effect is that irrespective of the sophestication of sampling used,
% the simplest sampling technique --- that of project based sampling --- is the best form of
% sampling, for a representative set.
% 
% This also applies immediately to operator selection as it is another kind of sampling on
% a smaller set. Hence it is no surprise that for larger samples, random sampling is able
% to trump operator selection on predicting the final result.
%
